Pseudobulk Differential Testing of Fovea vs Peripheral Cones

### 2022-09-23 supplemental_files/pseudobulk_cone_region.Rmd
pub update

We use the "ScaleData" function from Seurat to zero center and scale the counts for each dataset
#### PDE6G 
Top gene more highly expressed in the macula compared to the periphery. Seems pretty consistently higher across all the studies. 
```{r}
scEiaD__subset <- ScaleData(scEiaD__subset)
VlnPlot(scEiaD__subset, features = c('ENSG00000185527'), log = TRUE)

@@

#### All genes
```{r}
for (i in region_table %>% 
  filter(padj < 0.05) %>% 
  pull(Ensembl)){
  #print(i)
  gene_name <- region_table %>% filter(Ensembl == i) %>% pull(Gene)
  print(VlnPlot(scEiaD__subset, i, split.by = 'retina_region', group.by='study_accession', log = TRUE) + ggtitle(gene_name))
}
```

>>>>

We use the "ScaleData" function from Seurat to zero center and scale the counts for each dataset

#### PDE6G 
Top gene more highly expressed in the macula compared to the periphery. Seems pretty consistently higher across all the studies. 
```{r}
scEiaD__subset <- ScaleData(scEiaD__subset)
VlnPlot(scEiaD__subset, features = c('ENSG00000185527'), log = TRUE)

@@

#### All genes
```{r}
for (i in region_table %>% filter(padj < 0.05) %>% pull(Ensembl)){
  #print(i)
  gene <- region_table %>% filter(Ensembl == i) %>% pull(Gene)
  print(VlnPlot(scEiaD__subset, i, split.by = 'retina_region', group.by='study_accession', log = TRUE)  + ggtitle(gene))
}
```
